No proof nets for MLL with units\\[5pt]\Large Proof equivalence in MLL is \textsc{pspace}-complete

### 2014-01-19 main/LICS.tex
completed soundness proof

%% WORKING HERE

\begin{lemma}
If $\links\perm\links'$ are proof nets for $\itn G$ then $\coitn\links\perm\coitn{\links'}$.
\end{lemma}

\begin{IEEEproof}
The proof will consider the case where $\links\perm*\links'$; the general case follows by transitivity.
%
A single permutation $\links\sim\links'$ on proof nets may move a number of edge-gadgets $\itn{e_1},\dotso,\itn{e_n}$ in three ways: 1) out of the empire of a vertex-gadget $\int v$, 2) into the empire of a vertex-gadget $\int w$, or 3) both.
%
Then in both $\coitn\links$ and $\coitn{\links'}$ the edges $e_1$ through $e_n$ are mobile, since by Lemma~\ref{lem:appropriate edge weights} the empires of the vertex-gadgets $\itn v$ (in cases 1 and 3) and $\itn w$ (in cases 2 and 3) contain appropriate edge-gadgets other than $\itn{e_1}$ through $\itn{e_n}$ of sufficient combined weight.
%
It follows that in the graph $G$ the edges $e_1$ through $e_n$ can be moved away from $v$ and/or onto $w$ one at a time.

@@

\section{Conclusions}

>>>>

To show that rewiring corresponds to reconfiguration under $\coitn-$, we will use the following lemmata.

\begin{lemma}
\label{lem:rewiring within empire}
For a proof net $(\Gamma,\links)$ where $\links(a)=v$ and $w$ names a $\1$-occurrence in $\Gamma$, the following are equivalent:
%
\begin{enumerate}
	\item
$\links\perm*\links'$ where $\links'(a)=w$;
	\item
$w$ is in the empire of $a$; and
	\item
in any switching graph for $(\Gamma,\links)$, the path from $v$ to $w$ does not pass through $a$.
\end{enumerate}
\end{lemma}

\begin{IEEEproof}
By \cite[Proposition 2.a]{Bellin-vandeWiele-1995} 2 and 3 are equivalent.

Next, the empire of $a$ corresponds to the largest subproof $\Sigma$ in any $\Pi\toNet\links$ with as conclusion the introduction rule of $\named a\bot$.
%
By Definition~\ref{def:proofs to nets}, in the translation of $\Sigma$ to a net $\sigma$, $a$ may link anywhere in $\sigma$.
%
Then 2 implies 1.

Finally, if $\links'$ is a net, and for some switching of $\links$ the path from $v$ to $w$ passes through $a$, then in $\links'$ there is no path between $a$ and $v$ (and two paths between $a$ and $w$) for that switching; then 1 implies 3.
%
\end{IEEEproof}

\begin{lemma}
\label{lem:rewiring preserves empire}
Let $\links\perm*\links'$ by $\links(a)\neq\links'(a)$, and denote the empire of $a$ in $\links$ and $\links'$ by $\sigma$ and $\sigma'$ respectively; then $\sigma\perm*\sigma'$.
\end{lemma}

\begin{IEEEproof}
By Lemma~\ref{lem:rewiring empire} the empires $\sigma$ and $\sigma'$ contain the same $\1$-subformulae.
%
That they must share also any other subformula $A$ follows by the observation that $A\tn\1$ may replace $A$.
%
\end{IEEEproof}

\begin{lemma}
\label{lem:rewiring affects empires}
For proof nets $\links\perm*\links'$, let the empire of a given vertex $v$ in $\links$ be a net for the sequent $\Delta$, and in $\links'$, for $\Delta'$; then $\Delta\leq\Delta'$ or $\Delta\geq\Delta'$.
\end{lemma}

\begin{IEEEproof}
By \cite[Proposition 2.b]{Bellin-vandeWiele-1995} the empire of $v$ is determined by propagation from $v$: 1) through links; 2) up towards subformulae; 3) down from one subformula into a tensor; 4) down from all subformulae into a par; 5) but never down from $v$.
%
Let the link from $a$ be rewired, $\links(a)=w$ but $\links'(a)=w'$.
%
There are four cases.
%
\begin{enumerate}
	\item
If the empire of $v$ is propagated from $a$ to $w$ in $\links$, it includes the empire of $a$.
%
Then by Lemma~\ref{lem:rewiring preserves empire} $\Delta=\Delta'$.

	\item
If the empire of $v$ includes $w$ but not $w'$, then it is propagated through $a$ in $\links$ but not in $\links'$, so that $\Delta\geq\Delta'$.

	\item
If the empire of $v$ includes $w'$ but not $w$, then $\Delta\leq\Delta'$.

	\item
Otherwise, $\Delta=\Delta'$.
\end{enumerate}
\end{IEEEproof}

\begin{lemma}
\label{lem:soundness}
If $\links\perm\links'$ are proof nets for $\itn G$ then $\coitn\links\perm\coitn{\links'}$.
\end{lemma}

\begin{IEEEproof}
The proof will consider the case where $\links\perm*\links'$; the general case follows by transitivity.
%
By Lemma~\ref{lem:rewiring affects empires}, the empire of each vertex-gadget $\itn v$ contains either a subset of, a superset of, or exactly the same edge-gadgets in $\links'$ as it does in $\links$.
%
Let $\itn e_1$ through $\itn e_n$ be the edge-gadgets moving in or out of the empire of $\itn v$.
%
By Lemma~\ref{lem:appropriate edge weights} other edge-gadgets must fill the constraint elements of $\itn v$.
%
Then the corresponding edges $e_1$ through $e_n$ are mobile in $\coitn\links$ and it follows that $\coitn\links\perm\coitn{\links'}$ by moving each $e_i$ in turn, and repeating the same for other vertices.
%
\end{IEEEproof}

@@

\section{MLL proof equivalence is \textsc{pspace}-complete}

### 2014-01-19 main/scratch.tex
completed soundness proof

\usepackage{amsmath,amsthm}
\usepackage{mllequiv,willemtools}

@@

>>>>

\usepackage{amsmath,amssymb,amsthm}
\usepackage{mllequiv,willemtools}

@@

\[
	\lesssim \gtrsim
\[

\begin{lemma}
For a proof net $(\Gamma,\links)$, if the linking $\links'$ agrees with $\links$ on all values except $\links'(a)=v$, then $\links'$ is a proof net if and only if $v$ is in the empire of $a$ in $(\Gamma,\links)$.
%
%If $\links\perm*\links'$ by rewiring the link $\links(a)=v$ to $\links'(a)=w$, then $w$ is in the empire of $a$ in the proof net $\links$.
\end{lemma}

\begin{proof}
The empire of $a$ corresponds to the largest subproof $\Sigma$ in any $\Pi\toNet\links$ with as conclusion the introduction rule of $\named a\bot$.
%
In one direction, by Definition~\ref{def:proofs to nets} $a$ may link anywhere in a translation of $\Sigma$ to a net; if $\named v\1$ is in $\Sigma$, then $\links'$ is a net.
%
In the other direction, if $\links\perm*\links'$, then for any switching of $(\Gamma,\links')$ there is a path from $\links(a)=w$ to

%%Let $\sigma$ be the empire of $a$ in $(\Gamma,\links)$.
%%
%In one direction, if $v$ is in $\sigma$, then since $\sigma$ is a subnet, for any switching of $\sigma$ there is a path from $\links(a)$ to $v$ not passing through $a$.
%%
%Then if $\sigma'\perm*\sigma$ by 
%
% $\sigma$ minus the link $\edge a{\links(a)}$ is a subnet, 
%
%By definition, $\sigma$ is the largest subnet with $a$ as a port.
%%
%Then there is a proof $\Sigma\tonet\sigma$ with as conclusion the introduction rule for $\named a\bot$, which 1) is a subproof of some sequent proof $\Pi\tonet\links$, and 2) is the largest subproof of $\named a\bot$ among all $\Pi\tonet\links$.
%
%
%In one direction, if $\links'$ is a proof net, then $\links\perm*\links'$, and there is a $\Pi'\tonet\links'$ such that $\Pi\perm\Pi'$ by permuting the introduction rule for $\named a\bot$.
%%
%But since permuting this rule in $\Pi$ cannot give it a larger subnet than $\Sigma$ (by 2 above), $\named v\1$ must be in $\Sigma$, and $v$ in $\sigma$.
%
%By Definition~\ref{def:proofs to nets}

\end{proof}
